On the presentation of orthogonal groups over polynomial rings

### 2019-08-02 dl-paper.tex
Proving 5.30

\begin{lemma}
For $g_1 \in \overline{G}_M^{\geq 0}$ and $v\in \overline{V}$ one has $\overline{p}(t(g_1) \cdot v) = g_1 \cdot \overline{p}(v)$, where $t$ is the map from~\cref{lem:lemma32}.
\end{lemma}
\begin{proof}
 It suffices to verify this property for the generators $g = z_\alpha(f, \xi)$ of the subgroup $\overline{G}^{\geq 0}_M$ for all $f \in M[X]$, $\xi\in A[X]$.
 Set $I = M[X, X\inv]$. It is not hard to verify the assertion for the element $g_1 = z_\alpha(X^2f, aX^{-1}) \in \St(\Phi, B, I)$.
 Indeed, using the fact that $x_{\alpha}(X^2f) \in P_{-\alpha}(0)$ we obtain that
 \begin{multline}
  g_1 \cdot (g, [h], u) = x_{-\alpha}(-aX^{-1}) (x_\alpha(X^2f)x_{-\alpha}(aX^{-1})g, [h \cdot x_{-\alpha}(\tfrac{-aX^{-1}}{1+am})] )
\end{multline}

   \[ g_1 \cdot (g,\ [h],\ u) = () \]
 Consider the case $\xi = aX^{-1}$, $f = X^2f'$

 We verify the assertion by induction on the degree of $\xi$ in $X$ starting from $-1$.

 First of all, consider the case $\xi = aX$, $a\in A$. Notice that
 \[t(z_\alpha(f, aX)) = [x_{\beta}(X^{-1}) \cdot x_{\beta-\alpha}(a),\ x_{\alpha-\beta}(-fX) \cdot x_{-\beta}(afX^2)].\]
 \[ [x_\beta(X^{-1})^{x_{-\alpha}(aX)},\ x_{\alpha-\beta}(Xf)^{x_{-\alpha}(aX)}] \]
\end{proof}

\begin{multline}z_{\alpha+\beta}(f\xi, X) = x_\alpha(\epsilon f) \cdot x_{-\beta}(-fX) \cdot x_{\beta}(fX\xi^2) \cdot x_{\alpha+\beta}(f \xi) \cdot \\ \cdot z_\alpha(-\epsilon f, -\epsilon X\xi) \cdot
  x_{-\alpha}(-\epsilon fX^2\xi^2) \cdot x_{-\alpha-\beta}(- f X^2 \xi) \cdot z_{-\beta}(fX, -\xi)\end{multline}

\begin{multline}
 z_{\alpha+\beta}(f, aX) = x_\alpha(\epsilon Xf) x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon a) \cdot x_{-\alpha}(-\epsilon a^2fX) \cdot x_{-\alpha-\beta}(- f a^2X^2) \cdot z_{-\beta}(afX^2, -X^{-1})
\end{multline}

$s := fX$, $\eta := X^{-1}$, $\xi = aX$

>>>>

\begin{lemma}
For $g_1 \in \overline{G}_M^{\geq 0}$ and $v\in \overline{V}$ one has $\overline{p}(t(g_1) \cdot v) = g_1 \cdot \overline{p}(v)$, where $t$ is the map from~\cref{lem:lemma32}.
\end{lemma}
\begin{proof} 
It suffices to verify the assertion for the generators $g = z_\alpha(f, \xi)$ of the subgroup $\overline{G}^{\geq 0}_M$ for all $f \in M[X]$, $\xi\in A[X]$. We accomplished this by induction on the degree of $\xi$ in $X$.
It is obvious, that the assertion holds in the case $\xi = a \in A$.

Suppose that the assertion is true for all $g_1 = z_\alpha(f, \xi)$ with $\xi$ of degree $\leq n$.
Substituting $s := fX$, $\eta := X^{-1}$, $\xi := X\xi$ in~\eqref{Z5} we obtain the following equality in $\St(\Phi, A[X, X\inv], M[X, X\inv])$:
\begin{multline}
 z_{\alpha+\beta}(f, X\xi) = x_\alpha(\epsilon Xf) \cdot x_{-\beta}(-faX^2) \cdot x_{\beta}(af) \cdot x_{\alpha+\beta}(f) \cdot \\ \cdot z_\alpha(-\epsilon Xf, -\epsilon \xi) \cdot x_{-\alpha}(-\epsilon \xi^2fX) \cdot x_{-\alpha-\beta}(- f \xi^2X^2) \cdot z_{-\beta}(X^2f\xi, -X^{-1})
\end{multline}
It is not hard to verify the assertion for all the factors in the right hand side of the above expression
 (except for the fifth factor, for which it is precisely the inductive assumption). It remains to see that
  $t(z_\alpha(f, X\xi + a)) = x_\alpha(-a) \cdot t(z_\alpha(f, X\xi)) \cdot x_\alpha(a)$.
\end{proof}
